\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    citecolor=black,
}

\usepackage{doi}
\usepackage{natbib}
\bibliographystyle{unsrtnat}

% indentsection style
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left and one right
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% Remove numbers from publications
\makeatletter
\def\@bibitem#1{\item[]%
    \if@filesw\immediate\write\@auxout{\string \bibcite {#1}{\the\value{\@listctr }}}\fi\ignorespaces}
\makeatletter

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{John A. Karasinski, Ph.D.}}

	Mountain View, CA 94043
	\\
	(916) 467-2727\ \ \textbullet
	\ \ \href{mailto:karasinski@gmail.com}{karasinski@gmail.com}\ \ \textbullet
	\ \ \href{https://www.linkedin.com/in/jkarasinski/}{linkedin.com/in/jkarasinski}\ \ \textbullet
	\ \ \href{https://scholar.google.com/citations?user=06yynpAAAAAJ&hl=en}{Google Scholar}
\end{center}

\vspace{-0.5em}
\subsection*{Professional Summary}
\begin{indentsection}{\parindent}
A Human Factors researcher with a Ph.D. in Aerospace Engineering specializing in the intersection of human performance and space exploration. Focused on ensuring the safety, comfort, and mission success of astronauts by developing and designing crew-facing systems for next-generation spacecraft. Proven ability to translate technical requirements into intuitive and effective interfaces to solve the unique challenges of long-duration spaceflight.
\end{indentsection}

\hrule
\vspace{-0.5em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.05em 

	\item
	      \headerrow
	      {\textbf{NASA Ames Research Center}}
	      {\textbf{Moffett Field, CA}}
	      \\
	      \headerrow
		  {\emph{AST, Technical Management}}
	      {\emph{August 2023 -- Current}}
          \headerrow
		  {\emph{Research AST, Human/Machine Systems}} 
	      {\emph{September 2020 -- June 2022}}
		  \headerrow
	      {\emph{NASA Pathways Intern}}
	      {\emph{August 2017 -- September 2020}}
	      \headerrow
	      {\emph{Research Intern (Contractor via SJSU Research Foundation)}}
	      {\emph{June 2016 -- August 2017}}
	      \begin{itemize*}
                \item Lead human factors research and technology development within the Human Research Program and Mars Campaign Office to define human-system requirements for future deep space missions.
                \item Provide Human Health and Performance (HH\&P) insight for commercial partners (e.g., SpaceX, Blue Origin) to ensure Human Landing System (HLS) designs meet NASA's safety and usability standards.
                \item Conducted foundational research in human-computer interaction and human-automation integration, designing and building functional prototypes to demonstrate novel human-system capabilities.
                \item Contribute to research and development of Playbook, a mission-critical planning and execution tool that supports crew operations for analog missions (HERA, CHAPEA) and lunar payload deliveries (CLPS).
	      \end{itemize*}

	\item
	      \headerrow
	      {\textbf{Blue Origin}}
	      {\textbf{Kent, WA}}
	      \\
		  \headerrow
		  {\emph{Human Factors Engineer III}}
	      {\emph{June 2022 -- August 2023}}
	      \begin{itemize*}
                \item Served as the responsible engineer for Blue Origin's User Interface for Operational Displays Standard, applied across all programs (New Shepard, New Glenn, Blue Moon, Orbital Reef, etc.).
                \item Authored, evaluated, and verified human factors (HF) requirements for human-rated spacecraft, directly enhancing astronaut safety, comfort, and mission experience.
                \item Conducted comprehensive HF analyses, including task and human error analysis, to proactively identify and mitigate risks in crew procedures and system interfaces.
                \item Designed and executed high-fidelity HITL tests with astronaut-facing hardware to validate crew systems and inform design iterations.
	      \end{itemize*}

	\item
	      \headerrow
	      {\textbf{UC Davis Center for Human/Robotics/Vehicle Integration and Performance}}
	      {\textbf{Davis, CA}}
	      \\
	      \headerrow
	      {\emph{Senior Researcher}}
	      {\emph{June 2020 -- June 2022}}
		  \headerrow
	      {\emph{Graduate Student Researcher}}
	      {\emph{November 2013 -- June 2020}}
	      \begin{itemize*}
		      \item Developed and validated novel methods for the real-time assessment of operator performance, providing a foundation for adaptive training systems for long-duration spaceflight.
		      \item Engineered complex, high-fidelity simulations to analyze human-automation interaction and performance, supporting multiple human-subject research campaigns.
              \item Researched and applied computer-vision techniques for autonomous spacecraft rendezvous and docking, and utilized optimal control theory for spacecraft attitude pointing.
	      \end{itemize*}
	
	\item
	      \headerrow
	      {\textbf{Foodfully, Inc.}}
	      {\textbf{Davis, CA}}
	      \\
	      \headerrow
	      {\emph{Lead Software Developer}}
	      {\emph{2015 -- 2018}}
	      \begin{itemize*}
		      \item Led full-stack development (JavaScript, Meteor, MongoDB, React) for a consumer-facing application suite designed to reduce household food waste.
	      \end{itemize*}
	      
	\item
	      \headerrow
	      {\textbf{Teachers Curriculum Institute}}
	      {\textbf{Mountain View, CA}}
	      \\
	      \headerrow
	      {\emph{Software Developer}}
	      {\emph{2013 -- 2015}}
	      \begin{itemize*}
		      \item Developed interactive K-12 science curriculum and a comprehensive educational software suite.
	      \end{itemize*}

	\item
	      \headerrow
	      {\textbf{Handstand Inc.}}
	      {\textbf{Mountain View, CA}}
	      \\
	      \headerrow
	      {\emph{Content Administrator}}
	      {\emph{2011 -- 2012}}
	      \begin{itemize*}
		      \item Managed a team of 5 to build and curate a digital library of over 2,000 open-source STEM textbooks, achieving over 2 million views.
	      \end{itemize*}

	\item
	      \headerrow
	      {\textbf{University of California, Santa Cruz}}
	      {\textbf{Santa Cruz, CA}}
	      \\
	      \headerrow
	      {\emph{Undergraduate Student Researcher}}
	      {\emph{2009 -- 2013}}
	      \begin{itemize*}
	      	  \item Conducted high-energy gamma-ray timing analysis using data from the Fermi Gamma Ray Telescope for a senior thesis investigating potential signatures of dark matter.
		      \item Performed computer-aided testing, evaluation, and data analysis for the BARREL balloon campaign, a NASA mission studying relativistic electron loss events in Earth's radiation belts.
	      \end{itemize*}

\end{itemize}

\hrule
\vspace{-0.5em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em
	\item
	      \headerrow
	      {\textbf{University of California, Davis}}
	      {\textbf{Davis, CA}}
	      \\
	      \headerrow
	      {\emph{Ph.D. Mechanical and Aerospace Engineering}}
	      {\emph{2016 -- 2020}}
	      \\
	      \emph{Dissertation: \href{https://www.proquest.com/dissertations-theses/concurrent-bandwidth-feedback-complex-manual/docview/2449468766/se-2}{Concurrent Bandwidth Feedback for Complex Manual Control Tasks}}
	      \vspace{0.5em} % Adds a bit of space after the Ph.D. entry
	      \\
	      \headerrow
	      {\emph{M.S. Mechanical and Aerospace Engineering}}
	      {\emph{2013 -- 2016}}
	      \\
	      \emph{Thesis: \href{https://www.proquest.com/dissertations-theses/real-time-performance-feedback-manual-control/docview/1872339216/se-2}{Real-Time Performance Feedback for the Manual Control of Spacecraft}}
	\item
	      \headerrow
	      {\textbf{University of California, Santa Cruz}}
	      {\textbf{Santa Cruz, CA}}
	      \\
	      \headerrow
	      {\emph{B.S. Physics}}
	      {\emph{2008 -- 2012}}
	      \\
	      \emph{Thesis: A High Energy Timing Analysis with the Fermi Gamma-Ray Telescope}
\end{itemize}

\hrule
\vspace{-0.5em}
\subsection*{Technical Skills}

\begin{indentsection}{\parindent}
	\hyphenpenalty=1000
	\begin{description*}
		\item[Core Languages:] Python, Typescript/Javascript, R, C\# 
		\item[Human Factors:] Human-in-the-Loop (HITL) Simulation, Systems Safety \& Human Error Analysis, Human-Automation Integration, UX Research, Human-Centered Design, Mixed Model Statistical Analysis
		\item[Frameworks \& Engineering Tools:] React, MongoDB, Unity, MATLAB, Simulink, Ruby on Rails, \LaTeX, FORTRAN, \CPP
	\end{description*}
\end{indentsection}

\hrule
\vspace{-0.5em}
\subsection*{Selected Publications}

\nocite{*}
\renewcommand{\section}[2]{}%
\bibliography{publications}

\end{document}